Platforms for security update research

### 2014-02-05 platforms.tex
platforms: discuss JVM

\section{Java Virtual Machine (JVM)}

>>>>

\section{Java Virtual Machine (JVM)}
The Java Virtual Machine has a security manager and attempts to impose fine grained permissions on executing Java code~\cite{Gong1997} this is used by Java plugins in browsers to execute remote code without exposing the user to attacks.
Unfortunately there are many flaws in the JVM which have allowed arbitrary execute of code bypassing the security manager.
There are a list of vulnerabilities in the JVM \url{http://www.cvedetails.com/vulnerability-list/vendor_id-5/product_id-1526/opec-1/SUN-JRE.html}.
We also need the distribution of running versions over time.
